Discon analysis

### 2019-01-12 analysis/01_analysis.Rmd
Added preference experiment

files <- dir("../../adult_600_mumble/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_mumble/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

@@

```{r plot 2}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, trialType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
  arrange(workerid)

 # group_by(distribution, trialType, item) %>%
 # multi_boot_standard(col = "prop_correct")

>>>>

files <- dir("../../pilot_1_raw_data/production-results_framing/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../pilot_1_raw_data/production-results_framing/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

@@

```{r plot 2}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, trialType) %>%
  summarise(correct = mean(correct_target1)
            ) %>%
  gather(item, prop_correct, -distribution, -trialType) %>%
  arrange(workerid)

  group_by(distribution, trialType, item) %>%
  multi_boot_standard(col = "prop_correct")
